---
title: "P8105_HW5_hx2306"
author: "HuijunXiao"
date: "11/19/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 8, 
  fig.asp = .6,
  out.width = "90%")
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(ggplot2.continuous.colour = "viridis",
        ggplot2.continuous.fill = "viridis")
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

### Problem 1  
* Describe the raw data   
```{r}
homicides <- 
  read.csv("./dataset/homicide-data.csv") %>%
  janitor::clean_names() %>%  
  mutate(city_state = str_c(city,state,sep = ",")) %>%             #create a city_state variable
  mutate(status = case_when(
    disposition %in% 
      c("Closed without arrest","Open/No arrest") ~ "Unsolved",
    disposition == "Closed by arrest" ~ "Solved")) %>%             # categorize unsolved/ solved homicides 
  select(city_state,status) %>%
  subset(city_state != "Tulsa,AL")
```
    
* Summarize within cities to obtain the total number of homicides and the number of unsolved homicides   
```{r}
hom_summ <-                                                     #the total number of homicides
  homicides %>%
  group_by(city_state) %>%
  summarise(N_homicides = n())
unsolved_summ <-                                                #the number of unsolved homicides
  homicides %>%
  filter(status == "Unsolved") %>%
  group_by(city_state) %>%
  summarise(N_unsolved_homicides = n())
hom_city <-
  merge(hom_summ,unsolved_summ,by = "city_state",all = TRUE)

hom_city                                                        #city homicides summary table 
```
       
* Estimate the proportion of homicides that are unsolved    
```{r}
# prop.test function 
prop.test(
  unsolved_summ %>% 
    filter(city_state == "Baltimore,MD") %>%
    pull(N_unsolved_homicides),
  hom_summ %>%
    filter(city_state == "Baltimore,MD") %>%
    pull(N_homicides)) %>%
  broom::tidy()                                 #pull the estimated proportion and confidence intervals
```
    
* Proportion of unsolved homicides and the confidence interval for each city    
```{r}
city_summ <-
  hom_city %>%
  mutate(
    prop = map2(.x = N_unsolved_homicides,                #prop.test
                .y = N_homicides, 
                ~prop.test(x = .x, n = .y)),
    tidy = map(.x = prop,           
               ~broom::tidy(.x))) %>%                     #tidy
  unnest(tidy) %>%                                        #unnest tidy column 
  select(city_state, estimate, conf.low, conf.high)
  
city_summ
```
       
* City estimates and CIs plot    
```{r}
city_plot <-
  city_summ %>%
  mutate(city_state = fct_reorder(city_state,estimate)) %>%                 #organize cities 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low , ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.6, hjust = 1)) +
  ggtitle("Estimates and CIs for each city") +
  xlab("City, State") +
  ylab("Estimates") 
city_plot
```
       
### Problem 2     
* Start with a dataframe containing all file names     
```{r}
P2_data <-
  tibble(file = list.files("./p2data/"),
         path = str_c("./p2data/", file)) 
```
       
* Iterate over file names and read in data for each subject   
```{r, message=FALSE}
P2_iterate <-
  P2_data %>%
  mutate(data = map(.x = path, ~read_csv(.x)),
         arm = str_remove(path,".csv"),
         arm = str_remove(arm, "./p2data/")) %>%
  separate(arm, c("arm","id"), sep = "_") %>%
  mutate(arm = 
           ifelse(arm == "con","control","experiment"))%>%
  unnest(data)
```
     
* Tidy the result   
```{r, message=FALSE}
P2_tidy <-
  P2_iterate %>% 
  pivot_longer(
    week_1:week_8,
    values_to = "Observation",
    names_to = "Week") %>%
  mutate(Week = str_remove(Week, "week_")) %>%
  select(-path,-file)

P2_tidy
```
      
* Make a spaghetti plot   
```{r}
spaghetti <-
  P2_tidy %>%
  mutate(arm_new = arm) %>%
  unite("subjects",c(arm,id)) %>%
  ggplot() +
  geom_line(aes(x = Week, y = Observation, group = subjects, color = arm_new)) +
  ggtitle("Observations On Each Subject Over Time") +
  xlab("Week") +
  ylab("Observation") +
  scale_colour_discrete("Arm")
  
spaghetti  
```
      
From Spaghetti plot, we can tell that observation values of the experiment group increase from week 1 to week 8, but observation values of the control group do not change too much across eight weeks. The overall observation values of the experiment group are higher than those of the control group.      
      
### Problem 3   
```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

iris_with_missing

missing_rep = function(x) {
  if (is.numeric(x)) 
    {filled = replace(x, which(is.na(x)), mean(x, na.rm = TRUE))} 
  else if (is.character(x)) 
    {filled = replace(x, which(is.na(x)), "virginica")}
  filled 
  }

iris_df <-
  map(iris_with_missing, missing_rep) %>%
  bind_rows()

iris_df
```

     


